---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# speedytax

<!-- badges: start -->
[![R-CMD-check](https://github.com/jfq3/speedytax/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jfq3/speedytax/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of speedytax is to quickly import classification files generated with the QIIME2 classifier, the RDP Classifier and the USEARCH or vsearch sintax classifier as phyloseq tax_table objects.  

When importing RDP Classifier and sintax results, the confidence value can be specified on import. In the case of the QIIME2 classifier the confidence value must be given when calling the classifier.    

All ranks are filled, If a taxa is unclassified at a given rank(*i.e.* the confidence value at that rank is less than that specified), "the letter for the higher rank "uncl_" is prepended to the classification at the higher rank and copied to all lower ranks.  

For example, in the example below *Hyphomicrobiales* is classified to order and to uncl_*Hyphomicrobiales* at the family and genus levels.  

## Installation

You can install the development version of speedytax from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jfq3/speedytax")
```

## Example

This is an example of importing a classification file created with the RDP Classifier:

```{r example}
library(speedytax)
taxonomy_file <- read_tax_example("rdp_classifiification_table.tsv")
example_tax_table <- import_rdp_tax_table(in_file = taxonomy_file)
example_tax_table
```
