---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# speedytax

<!-- badges: start -->
<!-- badges: end -->

The goal of speedytax is to quickly import classification files generated with the QIIME2 classifier, the RDP Classifier and the vsearch sintax classifier as phyloseq tax_table objects.  

When importing RDP Classifier and sintax results, the confidence value can be specified on import. In the case of the QIIME2 classifier the confidence value must be given when calling the classifier.    

For each rank, a letter preface indicates the rank: "p_" for phylum, "c_" for class, *etc*. All ranks are filled, If a taxa is unclassified at a given rank(*i.e.* the confidence value at that rank is less than that specified), the letter for the higher rank is prepended to the classification at the higher rank.  

For example, if a taxa is classified as f_Oxalobacteraceae with a confidence of 0.7 but the confidence at the genus level is only 0.4, then its classification at the genus level will be g_f_Oxalobacteraceae. Tis is made clearer by examining the example below.    

## Installation

You can install the development version of speedytax from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jfq3/speedytax")
```

## Example

This is an example of importing a classification file created with the RDP Classifier:

```{r example}
library(speedytax)
taxonomy_file <- read_tax_example("rdp_classification_table.tsv")
example_tax_table <- import_rdp_tax_table(in_file = taxonomy_file)
example_tax_table
```
